\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-06-23 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating Section V

\subsubsection{Notation and organization}
We use boldfaced small letters for vectors, and boldfaced capital letters for matrices. The set of natural numbers, real numbers and complex numbers are denoted as $\mathbb{N}$, $\mathbb{R}$, and $\mathbb{C}$, respectively. The symbol $\nabla_{\bm{x}}$ denotes the Euclidean gradient operator with respect to (w.r.t.) the vector $\bm{x}$. Thus, $\nabla_{\bm{x}}\cdot$ stands for the divergence, and $\Delta_{\bm{x}}$ stands for the Laplacian w.r.t. vector $\bm{x}$. We use $\langle\cdot,\cdot\rangle$ to denote the standard Euclidean inner product. The real and imaginary parts of a complex number $z$ are denoted via $\Re(z)$ and $\Im(z)$, respectively. The uniform probability distribution over an interval $[a,b]$ is denoted as ${\rm{Unif}}\left([a,b]\right)$. The symbol $\propto$ denotes proportionality, $|\cdot|$ denotes the absolute value, $\|\cdot\|_{2}$ denotes the standard Euclidean 2-norm, $\otimes$ denotes the Kronecker product, $\det(\cdot)$ stands for the determinant, and the subscript $_{\sharp}$ denotes the pushforward of a PDF via a map. The $n\times n$ identity and zero matrices are denoted as $\bm{I}_{n}$ and $\bm{0}_{n\times n}$, respectively.

The rest of this paper is structured as follows. {\red{TBD}}

@@

\subsection{Synthetic Test System}\label{subsec:NumSimSynthetic}
We consider a power network with $n=20$ generators, and propagate the transient joint state PDFs supported over $\mathbb{T}^{20}\times\mathbb{R}^{20}$. We take the initial joint state PDF as
\[\rho_{0}(t=0,\theta(0),\omega(0)) = {\rm{Unif}}\left([0,2\pi)^{n}\right) \times {\rm{Unif}}\left([-0.1,0.1]\right).\]

>>>>

\subsubsection{Notation and organization}
We use boldfaced small letters for vectors, and boldfaced capital letters for matrices. The set of natural numbers, real numbers and complex numbers are denoted as $\mathbb{N}$, $\mathbb{R}$, and $\mathbb{C}$, respectively. The symbol $\nabla_{\bm{x}}$ denotes the Euclidean gradient operator with respect to (w.r.t.) the vector $\bm{x}$. Thus, $\nabla_{\bm{x}}\cdot$ stands for the divergence, and $\Delta_{\bm{x}}$ stands for the Laplacian w.r.t. vector $\bm{x}$. We use $\langle\cdot,\cdot\rangle$ to denote the standard Euclidean inner product. The real and imaginary parts of a complex number $z$ are denoted via $\Re(z)$ and $\Im(z)$, respectively. The uniform probability distribution over an interval $[a,b]$ is denoted as ${\rm{Unif}}\left([a,b]\right)$. Likewise, the $n$ dimensional uniform probability distribution over $[a,b]^{n}$ is denoted as ${\rm{Unif}}\left([a,b]^{n}\right)$. The symbol $\propto$ denotes proportionality, $|\cdot|$ denotes the absolute value, $\|\cdot\|_{2}$ denotes the standard Euclidean 2-norm, $\otimes$ denotes the Kronecker product, $\det(\cdot)$ stands for the determinant, and the subscript $_{\sharp}$ denotes the pushforward of a PDF via a map. The $n\times n$ identity and zero matrices are denoted as $\bm{I}_{n}$ and $\bm{0}_{n\times n}$, respectively.

The rest of this paper is structured as follows. Section \ref{sec:models} details the power system dynamics models at the microscopic or trajectory level, as well as at the macroscopic or ensemble level.

@@

\subsection{Synthetic Test System}\label{subsec:NumSimSynthetic}
We consider a power network with $n=20$ generators, and propagate the transient joint state PDFs supported over $\mathbb{T}^{20}\times\mathbb{R}^{20}$. We take the initial joint state PDF at $t=0$ as
\begin{align*}
\rho_{0}\equiv\rho(t=0,\theta(0),\omega(0)) = &\;{\rm{Unif}}\left([0,2\pi)^{n}\;\text{rad}\right)\\
	&\qquad\times {\rm{Unif}}\left([-0.1,0.1]\;\text{rad/s}\right),
\end{align*}
and the stochastic parameters as in Table \ref{table:ParamUncertaintiesSynthetic}.
